Complete Algebraic File Synchronization

### 2015-12-11 2015/paper.tex
Minor changes

@@

% New:
% better command (instruction) set
% simpler reconciliation algorithm
% proof of correctness

@@

\medskip

% Correctness of update detection
% -------------------------------

@@

\begin{myth}\label{update_works}
A sequence of commands returned by the update detector
when comparing $\FS^*$ to the original $\FS$
will not break $\FS$ if it is applied to it.
\end{myth}
\begin{proof}
Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
be the filesystem after the changes we intend to detect.
Let us assume that some mechanism recorded all changes that occurred
to $\FS$ until it reached the state $\FS^*$.
Our set if commands is sufficient to record any change, as
there are commands for every input and output type pair, therefore
we know that the changes can be recorded as a sequence of commands $S$
where $S\FS=\FS^*$.
Note that $S$ will not contain assertion commands, as they do not
represent an actual change in the filesystem.

>>>>

% TODO operation-based vs state-based

@@

% New:
% better command (instruction) set
% simpler reconciliation algorithm
% proof of correctness and completeness

% rigorous proof, non-trivial

% Update detection
% - ordering
% Reconciliation
% - conditional operation & inverse sequences

@@

\subsection{The Correctness of Update Detection}

@@

\begin{myth}\label{update_works}
A sequence of commands returned by the update detector
when comparing the non-broken $\FS^*$ to the original $\FS$
will not break $\FS$ if it is applied to it.
\end{myth}
\begin{proof}
Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
be the filesystem after the changes we intend to detect.
Let us assume that some mechanism recorded all changes that occurred
to $\FS$ until it reached the state $\FS^*$.
Our set if commands is sufficient to record any change, as
there are commands for every input and output type pair, therefore
we know that the changes can be recorded as a sequence of commands $S$
where $S\FS=\FS^*$.
Note that $S$ will not contain assertion commands, as they do not
represent an actual change in the filesystem.
